% resume.tex (clean, single-file, pdfLaTeX-friendly)
\documentclass[10pt]{article}

\usepackage[margin=0.7in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{titlesec}

\definecolor{Accent}{HTML}{1F4E79}

\setlist[itemize]{leftmargin=*, itemsep=2pt, topsep=2pt}
\titleformat{\section}{\large\bfseries\color{Accent}}{}{0pt}{}[\titlerule]
\titlespacing*{\section}{0pt}{8pt}{4pt}

\newcommand{\name}[1]{\begin{center}\LARGE\bfseries #1\end{center}}
\newcommand{\contact}[1]{\begin{center}\small #1\end{center}}
\newcommand{\sep}{\ \textbar\ }

\begin{document}
\pagestyle{empty}

% ===== Header =====
\name{Kaihong Deng}
\begin{center}\normalsize \textbf{Quantitative Developer \& Researcher}\end{center}
\contact{
Guangzhou, China (UTC+8)\sep
\href{mailto:kh.deng@foxmail.com}{kh.deng@foxmail.com}\sep
\href{https://doi.org/10.48550/arXiv.2512.22476}{arXiv:2512.22476}
}

% ===== Summary =====
\section*{Summary}
\begin{itemize}
  \item Seeking \textbf{Quant/Backtesting Engineer Intern (Remote)}; building an auditable backtesting + auto-tuning workflow for crypto perpetual futures.
  \item Focus: strict execution semantics (t$\rightarrow$t+1), realistic trading costs (fees/slippage/funding), walk-forward evaluation, reproducible artifacts.
  \item Delivery: can implement scoped modules (indicator/cost model/slippage model/validator/report) with tests and reproducible commands.
  \item Availability: Full-time (40+ hrs/week), start immediately (UTC+8).
\end{itemize}

% ===== Highlights =====
\section*{Highlights}
\begin{itemize}
  \item Strict backtesting with auditability: deterministic runs (seed), environment self-check signatures binding code+cost profile, and machine-readable artifacts.
  \item Realistic cost model per bar: fees + slippage + funding; multiple versioned cost profiles (e.g., conservative/high-leverage) for replay and sensitivity.
  \item WFE (walk-forward evaluation): rolling windows, consolidated ranking outputs (CSV/Excel), and robustness gates to reduce overfitting risk.
  \item Scalable experimentation: multi-process batch evaluation and Bayesian-style search (e.g., TPE) for efficient parameter tuning.
  \item Market/data \& validation integration: Binance Futures historical data; Gate.io perpetual testnet connectivity and live-style monitoring/report artifacts (no mainnet funds).
\end{itemize}

% ===== Skills =====
\section*{Skills}
\begin{tabularx}{\textwidth}{@{}l X@{}}
\textbf{Languages} & Python (3.10+), English (Technical reading/writing), SQL (basic), PowerShell (basic) \\
\textbf{Backtesting} & strict t$\rightarrow$t+1 semantics, cost modeling, WFE/robustness gates, metrics/reporting \\
\textbf{Optimization} & Optuna (TPE), Bayesian search, grid/random baselines \\
\textbf{Data} & pandas, NumPy, CSV/Parquet, time-series alignment, reproducibility controls \\
\textbf{Quality} & Git, pytest, type hints, ruff, pre-commit/CI gates, artifact/version traceability \\
\end{tabularx}

% ===== Projects =====
\section*{Selected Project}

\textbf{AutoQuant (Private) --- Crypto Perpetual Futures Backtesting \& Auto-Tuning System} \hfill \textit{2025--2026} \\
\textit{Python; strict execution engine + realistic costs + WFE + audit gates + Optuna}
\begin{itemize}
  \item Implemented a strict execution engine enforcing t$\rightarrow$t+1 semantics to reduce look-ahead bias; supports multi-timeframe signal pipelines.
  \item Integrated real-world cost modeling (fee, slippage, funding) and produced a cost breakdown for audits and sensitivity checks.
  \item Added walk-forward evaluation (sliding windows) and robustness gates to reduce \textit{best-of-N} overfitting risk.
  \item Automated parameter search with Optuna (TPE) and generated structured reports (Excel/CSV) for candidate ranking and validation.
  \item Designed reproducibility controls: self-check signatures bind code + cost profile; CI gates catch semantic drift (schema + no-lookahead tests).
  \item Built testnet-oriented validation and monitoring/report artifacts to evaluate execution constraints beyond pure backtests.
\end{itemize}

% ===== Experience =====
\section*{Experience}
\textbf{Independent Research Engineer (Quant)} \hfill \textit{Remote} \\
\textit{End-to-end ownership (design $\rightarrow$ implementation $\rightarrow$ verification $\rightarrow$ audit)}
\begin{itemize}
  \item Built and iterated a research workflow that prioritizes correctness and reproducibility before scaling experiments.
  \item Maintained an append-only decision log and traceable artifacts for each experiment run.
\end{itemize}

% ===== Education =====
\section*{Education}
\textbf{Guangzhou College of Commerce (GCC)} \hfill \textit{2023--2027 (expected)} \\
B.S. Candidate in Artificial Intelligence

% ===== Work Samples =====
\section*{Work Samples}
\begin{itemize}
  \item Preprint: \href{https://doi.org/10.48550/arXiv.2512.22476}{AutoQuant: An Auditable Expert-System Framework for Execution-Constrained Auto-Tuning in Cryptocurrency Perpetual Futures} (arXiv:2512.22476).
  \item Additional technical documentation and sample reports can be provided upon request.
\end{itemize}

\end{document}
